Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-27 paper.tex
Update numbers in evaluation to match new data

% TODO: check over/underfull boxes
% TODO: move references to new page
% TODO: ensure that numbers in evaluation discussion match the final data

@@

Fig.~\ref{fig:trans} shows that the incremental algorithm has a sizeable advantage over the naive algorithm.
The scales are logarithmic, with each dotted horizontal line representing an 8-fold increase.
Hence, for $2^{5} = 32$ hypotheses and $a = 0$, incremental forward reasoning is over 38 times faster than naive forward reasoning.
The difference for $a = 100$ is even larger.

These results are explained by the number of times either algorithm matches a premise against a hypothesis.
The naive algorithm iterates over the context, which initially contains $n$ hypotheses, and compares all hypotheses pairwise.
This is repeated approximately for each of the $n(n-1)/2$ added hypotheses, so $\bigO(n^4)$ match operations are performed.
By contrast, the incremental algorithm considers each hypothesis only once, matching it against both slots and then comparing it with at most $n$ other hypotheses.
It therefore performs only $\bigO(n^2)$ match operations.

>>>>

% TODO: check over/underfull boxes
% TODO: move references to new page

@@

Fig.~\ref{fig:trans} shows that the incremental algorithm has a sizeable advantage over the naive algorithm.
The scales are logarithmic, with each dotted horizontal line representing an 8-fold increase.
Hence, for $2^{5} = 32$ hypotheses and $a = 0$, incremental forward reasoning is over 42 times faster than naive forward reasoning.
The speedup for $a = 100$ is around 99x, with naive forward reasoning taking over 6 minutes.

These results are largely explained by the number of times either algorithm matches a premise against a hypothesis.
The naive algorithm iterates over the context, which initially contains $n$ hypotheses, and compares all hypotheses pairwise.
This is repeated approximately for each of the $n(n-1)/2$ added hypotheses, so $\bigO(n^4)$ match operations are performed.
By contrast, the incremental algorithm considers each hypothesis only once, matching it against both slots and then comparing it with at most $n$ other hypotheses.
It therefore performs only $\bigO(n^2)$ match operations.
